---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# missingGroup

<!-- badges: start -->
<!-- badges: end -->

`missingGroup` is an R package designed to facilitate the analysis of missing values in datasets. It provides a straightforward and efficient way to group a data frame by a specified column and then calculate the count of missing values in all other columns for each group.

## Installation

You can install the development version of missingGroup like so:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/missingGroup")
```

## Example

Here are a few examples that showcase the usage of these functions

### Example 1: Basic Use 

This is a basic example which shows you how to use the function:

```{r example}

library(missingGroup)
library(dplyr)

exists("count_all_missing_by_group")
# Using the airquality dataset
count_all_missing_by_group(airquality, Month)

```

### Example 2: Piping a Dataset

```{r}

# Piping the dataset into the function
airquality |> count_all_missing_by_group(Month)

```

### Example 3: Keeping the Grouping

```{r}

# Keeping the output grouped
count_all_missing_by_group(airquality, Month, .groups = "keep")

```

